The Small World Network Effect in Software Project Teams \author{Kevin Peterson\\ \small \texttt{pete1968@umn.edu} }

### 2013-11-21 paper/main.tex
Fixed a typo.

\noindent\\\textit{Q1: How do development teams collaborate and share ideas?}\\
\noindent\\\textit{Q2: Do teams generally remain intact over multiple projects, or do members often shuffle and re-combine?}\\
\noindent\\\textit{Q3: When assembling a team, which is preferred -- members familiar with each other, or members familiar with the task or project.}\\
\noindent\\\textit{Q4: What are some characteristics of a high performing team?}\\
\noindent\\\textit{Q5: In your experience, is it better to (A) keep an innovative team intact, (B) periodically bring in new members or re-assign exising members, or (C) split up and disperse the team to as many other projects as possible?}\\

>>>>

\noindent\\\textit{Q1: How do development teams collaborate and share ideas?}\\
\noindent\\\textit{Q2: Do teams generally remain intact over multiple projects, or do members often shuffle and re-combine?}\\
\noindent\\\textit{Q3: When assembling a team, which is preferred -- members familiar with each other, or members familiar with the task or project.}\\
\noindent\\\textit{Q4: What are some characteristics of a high performing team?}\\
\noindent\\\textit{Q5: In your experience, is it better to (A) keep an innovative team intact, (B) periodically bring in new members or re-assign existing members, or (C) split up and disperse the team to as many other projects as possible?}\\
